---
title: "Tourism in India Project Report"
author: "Group 16:- 
Chandan Kumar Singh (231080030),

Omkar Yadav (231080062),

Soumen Konai (231080091),

Ashwani Kumar (231080025),

Instructor:- 
Prof. Dootika Vats
"
output:
  html_document:
    df_print: paged
---

```{r}
#| echo: FALSE
#| eval: TRUE
#| warning: FALSE
library(tidyverse)
library(rvest)
library(dplyr)
library(imager)
library(DT)
library(ggplot2)
library(shiny)
library(htmltools)
```

# Introduction

This report provides a detailed explanation of the "Tourism in India" Shiny app. The app is designed to display tourism-related data and visualizations for various parts of India, motorcycle tours, and travel information by month.

India is a land of diverse cultures, landscapes, and traditions which offers a captivating tapestry for tourists. Our project, "Exploring India's Hidden Gems," seeks to showcase the uncharted beauty and rich heritage of this incredible country. With a focus on sustainable and responsible tourism, we aim to promote lesser-known destinations, unique cultural experiences, and eco-friendly practices. Through this project, we aspire to foster economic growth in local communities, preserve India's natural wonders, and provide travelers with unforgettable journeys that go beyond the usual tourist trail. Join us on a transformative voyage through the heart of India and discover its untold stories.

# Objective

This project aims to provide users with an immersive experience by offering a curated selection of the top ten most favorable places in each selected area.

Our Shiny app, 'Discover India's Treasures,' is a user-friendly platform designed to help travelers and enthusiasts explore the breathtaking beauty and cultural richness of India's diverse states and main regions. 

# Data Extraction and Preprocessing

We are extracting data from "https://en.wikipedia.org/wiki/Tourism_in_India".

Basically we collect the pictures name and the picture url.

We extracted tables as follows:-

table_1 for Foreign tourist arrivals in India (1997–20222).

table_2 for Foreign exchange earnings from tourism in India (1997–2020).

table_3 for Source countries for foreign tourist arrivals in India in 2019.

table_4 for Share of top 10 states/UT's of India in number of foreign tourist visits in 2017.

table_5 for Share of top 10 states/UT's of India in number of domestic tourist visits in 2017.



```{r}
#| echo: FALSE
#| eval: TRUE
html <- read_html("https://en.wikipedia.org/wiki/Tourism_in_India")

table_data <- html %>%
  html_table()

# Foreign tourist arrivals in India (1997–20222).
table_1 <- table_data[[4]]

# Foreign exchange earnings from tourism in India (1997–2020).
table_2 <- table_data[[5]]

# Source countries for foreign tourist arrivals in India in 2019.
table_3 <- table_data[[6]]

# Share of top 10 states/UT's of India in number of foreign tourist visits in 2017.
table_4 <- table_data[[8]]

# Share of top 10 states/UT's of India in number of domestic tourist visits in 2017.
table_5 <- table_data[[9]]



```


The app fetches data from web sources, primarily Wikipedia. It retrieves tables and images related to tourism in India.

we also try to scrap the places description and put this as a link in shiny app.

final_table for scrapped_final_table .

```{r}
#| echo: FALSE
#| eval: TRUE

data_img <- html %>%
  html_elements(".mw-file-element") %>%
  html_attr("src")

data_img <- data_img[29:110]
# data_img

data_place <- html %>% html_elements(".gallerytext") %>% html_text()
data_place <- data_place[1:82]
Place_to_Visit <- c()
for(i in 1:82)
{
  data_place[i] <- substring(data_place[i],first = 2)
  Place_to_Visit[i] <- gsub(pattern = "\n\n\t\t\t",replacement = "",x = data_place[i])
}

# we can also use this for collecting names
# html %>% html_elements(".gallerytext") %>% html_text2()

# Place_to_Visit

url_img <- c()
for(i in 1:82)
{
  
  url_img[i] <- paste0("https:",data_img[i])
}
# url_img
# a <- load.image(url_img[1])
# plot(a)


#data <- tibble(Place_to_Visit,url_img)
#view(data)  


d <- html %>% html_elements(".gallerytext a") %>% html_attr("href")
# d

link_n <- c(d[1],d[3],d[5],d[7],d[9],d[10],d[12],
            d[13],d[15],d[17],d[19],d[21],d[23],
            d[24],d[25],d[26],d[27],d[29],d[30])
link_s <- c(d[32],d[33],d[36],d[38],d[40],d[42],d[43],d[44],
            d[45],d[47],d[48],d[50],d[52],
            d[53],d[54])
link_c <- c(d[55],d[57],d[59],d[60],d[61],d[62],d[65],
            d[66],d[68],d[69],d[71],d[73],
            d[75])
link_w <- c(d[76],d[77],d[78],d[80],d[81],d[82],
            d[83],d[84],d[85],d[87],
            d[89],d[91],d[92],d[93],
            d[95],d[96])
link_e <- c(d[98],d[100],d[103],"Rainbow Waterfalls",
            d[105],d[108],d[109],d[110],d[111],
            d[112],d[113],d[114],"Sri_Mayapur_Chandrodaya_Mandir")
link_ne <- c(d[116],d[118],d[120],d[121],
             d[122],d[123])

description <- c(link_n,link_s,link_c,link_w,link_e,link_ne)
# description

url_place_description <- c()
for(i in 1:82)
{
  
  url_place_description[i] <- paste0("https://en.wikipedia.org/",description[i])
}
# url_place_description


final_table <- tibble(Place_to_Visit,url_img,url_place_description)

dis <- NULL
for (i in 1:82)
{
  dis[i] <- paste0("<a href='",final_table$url_place_description[i],"' target='_blank'>Details</a>")
}




# if you want to see the table realted the webpage the you can run the below code.
# for getting more information in (readable) table format
#  table <- c()
#  for(i in 1:84)
#  {

#    table[i] <- read_html(url_img_description[i]) %>% 
#    html_table()
#   }


```

## Data Visualization and Analysis

The app uses a combination of ggplot2 and DT for data visualization and analysis. Each of the following sections corresponds to a specific tab within the app.

# Foreign Tourist Arrivals in India (1997 -- 2022)

```{r}
#| echo: FALSE
#| eval: TRUE
table_1
```

## Data Visualization

The "Foreign tourist arrivals in India (1997--2022)" tab presents a line plot showing the trend in foreign tourist arrivals over the years.

```{r}
#| echo: FALSE
#| eval: TRUE


data <- table_1
ggplot(data = data) +
        geom_line(mapping = aes(x = Year, y = `Arrivals (millions)`), linetype = 1, linewidth = 1, color = "red")
```

## Insights

On an average the number of people Arrived (millions) (1997 - 2022)

```{r}
#| echo: FALSE
#| eval: TRUE
table_1$`Arrivals (millions)` <- as.numeric(table_1$`Arrivals (millions)`)
mean(table_1$`Arrivals (millions)`) 
```

we can see that in 2019 because of covid pandemic the number arrivals go down and after 2021 there is increment in number of arrivals

# Foreign exchange earnings from tourism in India (1997--2020)

```{r}
#| echo: FALSE
#| eval: TRUE
table_2
```

## Data Visualization

The "Foreign exchange earnings from tourism in India (1997--2020)" tab displays a bar chart showing earnings in Indian Rupees over the years.

```{r}
#| echo: FALSE
#| eval: TRUE
data <- table_2
data$`Earnings (₹ crores)` <- as.numeric(gsub(",", "", gsub("−", "-", data$`Earnings (₹ crores)`)))
      # Create a bar plot
      barplot(data$`Earnings (₹ crores)`, names.arg = data$Year, col = "blue", main = "Earnings Over the Years",
              xlab = "Year", ylab = "Earnings in ₹ Crores")
```

# Source countries for foreign tourist arrivals in India in 2019.

```{r}
#| echo: FALSE
#| eval: TRUE
table_3
```

## Data Visualization

```{r}
#| echo: FALSE
#| eval: TRUE
data <- table_3
data <- data[-c(12),]
      
      # Assuming your data is in a tibble named table_2
      data$Number <- as.numeric(gsub(",", "", data$Number))
      barplot(data$Number, names.arg = data$Country, col = "blue", main = "Number of People",
              xlab = "Country", ylab = "Number")
```

## Insights
Bangladesh is the topmost country with 23.58 % share.

# Share of top 10 states/UTs of India in number of foreign tourist visits in 2017.

```{r}
#| echo: FALSE
#| eval: TRUE
table_4
```

## Data Visualization

```{r}
#| echo: FALSE
#| eval: TRUE
data <- table_4
data <- data[c(1:10),]
      
      # Assuming your data is in a tibble named table_2
      data$Number <- as.numeric(gsub(",", "", data$Number))
      barplot(data$Number, names.arg = data$`State/Union Territory`, col = "blue", main = "Share of top 10 states/UTs of India in number of foreign tourist visits in 2017",
              xlab = "State/Union Territory", ylab = "NUmber")
```

## Insights
Maharashtra of India is the topmost in number of foreign tourist visits with 18.9 %.

# Share of top 10 states/UTs of India in number of domestic tourist visits in 2017.

```{r}
#| echo: FALSE
#| eval: TRUE
table_5
```

## Data Visualization

```{r}
#| echo: FALSE
#| eval: TRUE
data <- table_5
data <- data[c(1:10),]
      
      # Assuming your data is in a tibble named table_2
      data$Number <- as.numeric(gsub(",", "", data$Number))
      barplot(data$Number, names.arg = data$`State/Union Territory`, col = "blue", main = "Share of top 10 states/UTs of India in number of domestic tourist visits in 2017",
              xlab = "State/Union Territory", ylab = "NUmber")
      
```

## Insights
Tamil Nadu of India is the topmost in number of domestic tourist visits with 20.9 %.

# Final Table

```{r}
#| echo: FALSE
#| eval: TRUE
final_table <- tibble(final_table$Place_to_Visit,dis) 
colnames(final_table)[colnames(final_table) == "final_table$Place_to_Visit"] <- "Place_to_Visit"
colnames(final_table)[colnames(final_table) == "dis"] <- "discription_link"
final_table
```


# Main Parts of India

The "Main Parts of India" tab provides users with data related to different parts of India, including North, South, Central, West, East, and Northeast India. Users can select a specific region and view associated data.

## Scrapped Tables

## North India

```{r}
#| echo: FALSE
#| eval: TRUE

North_India <- tibble(Place_to_Visit[1:19],url_img[1:19],url_place_description[1:19])
colnames(North_India)[colnames(North_India) == "Place_to_Visit[1:19]"] <- "Data_Type"
colnames(North_India)[colnames(North_India) == "url_img[1:19]"] <- "Picture_URL"
North_India
```

## South India
```{r}
#| echo: FALSE
#| eval: TRUE
South_India <- tibble(Place_to_Visit[20:34],url_img[20:34],url_place_description[20:34])
colnames(South_India)[colnames(South_India) == "Place_to_Visit[20:34]"] <- "Data_Type"
colnames(South_India)[colnames(South_India) == "url_img[20:34]"] <- "Picture_URL"
South_India
```

## Central India
```{r}
#| echo: FALSE
#| eval: TRUE
Central_India <- tibble(Place_to_Visit[35:47],url_img[35:47],url_place_description[35:47])
colnames(Central_India)[colnames(Central_India) == "Place_to_Visit[35:47]"] <- "Data_Type"
colnames(Central_India)[colnames(Central_India) == "url_img[35:47]"] <- "Picture_URL"
Central_India
```

## West India
```{r}
#| echo: FALSE
#| eval: TRUE
West_India <- tibble(Place_to_Visit[47:63],url_img[47:63],url_place_description[47:63])
colnames(West_India)[colnames(West_India) == "Place_to_Visit[47:63]"] <- "Data_Type"
colnames(West_India)[colnames(West_India) == "url_img[47:63]"] <- "Picture_URL"
West_India
```

## East India
```{r}
#| echo: FALSE
#| eval: TRUE
East_India <- tibble(Place_to_Visit[63:76],url_img[63:76],url_place_description[63:76])
colnames(East_India)[colnames(East_India) == "Place_to_Visit[63:76]"] <- "Data_Type"
colnames(East_India)[colnames(East_India) == "url_img[63:76]"] <- "Picture_URL"
East_India
```
## NorthEast India
```{r}
#| echo: FALSE
#| eval: TRUE
NorthEast_India <- tibble(Place_to_Visit[76:82],url_img[76:82],url_place_description[76:82])
colnames(NorthEast_India)[colnames(NorthEast_India) == "Place_to_Visit[76:82]"] <- "Data_Type"
colnames(NorthEast_India)[colnames(NorthEast_India) == "url_img[76:82]"] <- "Picture_URL"
NorthEast_India
```



# States/UT's
India is a diverse country so every state/UT's has some beautiful places to vist.

So we scrapped the top ten most favorable places to visit for each state.

## Scrapped Tables

## Andhra Pradesh

```{r}
#| echo: FALSE
#| eval: TRUE
# Andhra_Pradesh

##### for url of photo...............

html_Andhra <- read_html("https://en.wikipedia.org/wiki/Tourism_in_Andhra_Pradesh")

html_Andhra1 <- html_Andhra%>%html_elements(".mw-file-element")%>%html_attr("src")

html_Andhra1 <- html_Andhra1[2:11]
url_img <- c()
for(i in 1:10)
{
  
  url_img[i] <- paste0("https:",html_Andhra1[i])
}


###### for name of photo..............

html_Andhra2 <- html_Andhra%>%html_elements(".mw-default-size")%>%html_text()

html_Andhra2[1]= "Highest Man Made Stone Nandi"

Place_to_Visit <- html_Andhra2[1:10]

Andhra_Pradesh <- data.frame(Place_to_Visit,url_img)

Andhra_Pradesh <- tibble(Place_to_Visit[1:10],url_img[1:10])
colnames(Andhra_Pradesh)[colnames(Andhra_Pradesh) == "Place_to_Visit[1:10]"] <- "Data_Type"
colnames(Andhra_Pradesh)[colnames(Andhra_Pradesh) == "url_img[1:10]"] <- "Picture_URL"
Andhra_Pradesh

```

## Bihar
```{r}
#| echo: FALSE
#| eval: TRUE
#  Bihar

##### for url of photo...............

html_Bihar <- read_html("https://en.wikipedia.org/wiki/Tourism_in_Bihar")

html_Bihar1 <- html_Bihar%>%html_elements(".mw-file-element")%>%html_attr("src")

html_Bihar1 <- html_Bihar1[1:10]

url_img <- c()
for(i in 1:10)
{
  
  url_img[i] <- paste0("https:",html_Bihar1[i])
}

###### for name of photo..............

html_Bihar2 <- html_Bihar%>%html_elements(".mw-default-size")%>%html_text()

html_Bihar2[5]= "Maha Bodhi Temple, Bodhgaya"

html_Bihar2[6]="Nalanda Mounds"

html_Bihar2[7]="Vikramshila"

html_Bihar2[8]="Old City Walls at Rajgir"

html_Bihar2[9]="Kesariya Stupa -kesariya- east champaran"

html_Bihar2[10]=" Ashokan Pillar Vaishali "

Place_to_Visit <- html_Bihar2

Bihar <- data.frame(Place_to_Visit,url_img)

Bihar <- tibble(Place_to_Visit[1:10],url_img[1:10])
colnames(Bihar)[colnames(Bihar) == "Place_to_Visit[1:10]"] <- "Data_Type"
colnames(Bihar)[colnames(Bihar) == "url_img[1:10]"] <- "Picture_URL"
Bihar
```
## Chattisgarh

```{r}
#| echo: FALSE
#| eval: TRUE
#  chattisgarh

##### for url of photo...............

html_chattisgarh <- read_html("https://en.wikipedia.org/wiki/Tourism_in_Chhattisgarh")

html_chattisgarh1 <- html_chattisgarh%>%html_elements(".mw-file-element")%>%html_attr("src")

html_chattisgarh1 <- html_chattisgarh1[3:12]

url_img <- c()
for(i in 1:10)
{
  
  url_img[i] <- paste0("https:",html_chattisgarh1[i])
}


###### for name of photo..............

html_chattisgarh2 <- html_chattisgarh%>%html_elements(".mw-default-size")%>%html_text()
html_chattisgarh2 <- c(html_chattisgarh2[1:9])
html_chattisgarh3 <- c("Chitrakot_waterfalls")
html_chattisgarh4 <- c(html_chattisgarh3,html_chattisgarh2)
html_chattisgarh4[7] <- "Baloda-bazar"

Place_to_Visit <- html_chattisgarh4[1:10]

chattisgarh <- data.frame(Place_to_Visit,url_img)

chattisgarh <- tibble(Place_to_Visit[1:10],url_img[1:10])
colnames(chattisgarh)[colnames(chattisgarh) == "Place_to_Visit[1:10]"] <- "Data_Type"
colnames(chattisgarh)[colnames(chattisgarh) == "url_img[1:10]"] <- "Picture_URL"
chattisgarh
```

## Gujarat
```{r}
#| echo: FALSE
#| eval: TRUE
# Gujarat

##### for url of photo...............

html_Gujarat <- read_html("https://en.wikipedia.org/wiki/Tourism_in_Gujarat")

html_Gujarat1 <- html_Gujarat%>%html_elements(".mw-file-element")%>%html_attr("src")

html_Gujarat1 <- html_Gujarat1[4:13]

url_img <- c()
for(i in 1:10)
{
  
  url_img[i] <- paste0("https:",html_Gujarat1[i])
}

###### for name of photo..............

html_Gujarat2 <- html_Gujarat%>%html_elements(".mw-default-size")%>%html_text()

Place_to_Visit <- html_Gujarat2[1:10]

Gujarat <- data.frame(Place_to_Visit,url_img)

Gujarat <- tibble(Place_to_Visit[1:10],url_img[1:10])
colnames(Gujarat)[colnames(Gujarat) == "Place_to_Visit[1:10]"] <- "Data_Type"
colnames(Gujarat)[colnames(Gujarat) == "url_img[1:10]"] <- "Picture_URL"
Gujarat
```

## Uttar Pradesh
```{r}
#| echo: FALSE
#| eval: TRUE
# Uttar_pradesh

##### for url of photo...............

html_Uttar_pradesh <- read_html("https://en.wikipedia.org/wiki/Tourism_in_Uttar_Pradesh")

html_Uttar_pradesh1 <- html_Uttar_pradesh%>%html_elements(".mw-file-element")%>%html_attr("src")

html_Uttar_pradesh1[1] <- html_Uttar_pradesh1[30]

html_Uttar_pradesh1[5] <- html_Uttar_pradesh1[18]

html_Uttar_pradesh1[9] <- html_Uttar_pradesh1[29]

html_Uttar_pradesh1[3] <- html_Uttar_pradesh1[41]

html_Uttar_pradesh1[6] <- html_Uttar_pradesh1[25]

html_Uttar_pradesh1<- html_Uttar_pradesh1[1:10]

url_img <- c()
for(i in 1:10)
{
  
  url_img[i] <- paste0("https:",html_Uttar_pradesh1[i])
}

###### for name of photo..............
html_Uttar_pradesh <- c()
html_Uttar_pradesh[1] <- "Triveni Sangam, Allahabaad"
html_Uttar_pradesh[2] <- "Taj_Mahal, Agra"
html_Uttar_pradesh[3] <- "Fatehpur Sikri"
html_Uttar_pradesh[4] <- "Prem_mandir"
html_Uttar_pradesh[5] <- "Agra Fort"
html_Uttar_pradesh[6] <- "Naini_Bridge,Allahabaad"
html_Uttar_pradesh[7] <- "Varanasiganga"
html_Uttar_pradesh[8] <- "Kumbhmela"
html_Uttar_pradesh[9] <- "Anand_Bhawan"
html_Uttar_pradesh[10] <- "Ashtapad Hastinapur"

Place_to_Visit <- html_Uttar_pradesh

Uttar_pradesh <- data.frame(Place_to_Visit,url_img)

Uttar_pradesh <- tibble(Place_to_Visit[1:10],url_img[1:10])
colnames(Uttar_pradesh)[colnames(Uttar_pradesh) == "Place_to_Visit[1:10]"] <- "Data_Type"
colnames(Uttar_pradesh)[colnames(Uttar_pradesh) == "url_img[1:10]"] <- "Picture_URL"
Uttar_pradesh
```

## Karnataka
```{r}
#| echo: FALSE
#| eval: TRUE
# Karnataka

##### for url of photo...............

html_Karnataka <- read_html("https://en.wikipedia.org/wiki/Tourism_in_Karnataka")

html_Karnataka1 <- html_Karnataka%>%html_elements(".mw-file-element")%>%html_attr("src")
html_Karnataka1 <- html_Karnataka1[70:79]
url_img <- c()
for(i in 1:10)
{
  
  url_img[i] <- paste0("https:",html_Karnataka1[i])
}

###### for name of photo..............

html_Karnataka2 <- html_Karnataka%>%html_elements(".mw-default-size")%>%html_text()
html_Karnataka2 <- html_Karnataka2[5:14]
Place_to_Visit <- html_Karnataka2
Karnataka <- data.frame(Place_to_Visit,url_img)

Karnataka <- tibble(Place_to_Visit[1:10],url_img[1:10])
colnames(Karnataka)[colnames(Karnataka) == "Place_to_Visit[1:10]"] <- "Data_Type"
colnames(Karnataka)[colnames(Karnataka) == "url_img[1:10]"] <- "Picture_URL"
Karnataka
```

## Jharkhand
```{r}
#| echo: FALSE
#| eval: TRUE
# Jharkhand  

##### for url of photo...............

html_Jharkhand  <- read_html("https://en.wikipedia.org/wiki/Tourism_in_Jharkhand")

html_Jharkhand1 <- html_Jharkhand %>%html_elements(".mw-file-element")%>%html_attr("src")

html_Jharkhand1 <- html_Jharkhand1[-c(8)]

html_Jharkhand1 <- html_Jharkhand1[1:10]

url_img <- c()

for(i in 1:10)
{
  
  url_img[i] <- paste0("https:",html_Jharkhand1[i])
}

###### for name of photo..............

html_Jharkhand2 <- html_Jharkhand%>%html_elements(".mw-default-size")%>%html_text()

Place_to_Visit <- html_Jharkhand2[1:10]

Jharkhand <- data.frame(Place_to_Visit,url_img)

Jharkhand <- tibble(Place_to_Visit[1:10],url_img[1:10])
colnames(Jharkhand)[colnames(Jharkhand) == "Place_to_Visit[1:10]"] <- "Data_Type"
colnames(Jharkhand)[colnames(Jharkhand) == "url_img[1:10]"] <- "Picture_URL"
Jharkhand
```

## Goa
```{r}
#| echo: FALSE
#| eval: TRUE
# Goa  

##### for url of photo...............

html_Goa  <- read_html("https://en.wikipedia.org/wiki/Tourism_in_Goa")

html_Goa1 <- html_Goa%>%html_elements(".mw-file-element")%>%html_attr("src")

html_Goa1 <- html_Goa1[-c(9:12)]

html_Goa1 <- html_Goa1[1:10]
url_img <- c()
for(i in 1:10)
{
  
  url_img[i] <- paste0("https:",html_Goa1[i])
}

###### for name of photo..............

html_Goa2 <- html_Goa%>%html_elements(".thumb.tright")%>%html_text()

foo_Goa <- strsplit(html_Goa2, ",")

html_Goa3 <- foo_Goa[[1]][2:7]

html_Goa4 <- c("Goa_panoramio")

html_Goa2 <- c(html_Goa4,c( html_Goa3))

html_Goa2[8] <- "Baga Beach in North Goa"

html_Goa2[9] <- "Bogmalo beach in South Goa"

html_Goa2[10] <- "Glassy Tiger"

Place_to_Visit <- html_Goa2

Goa <- data.frame(Place_to_Visit,url_img)

Goa<- tibble(Place_to_Visit[1:10],url_img[1:10])
colnames(Goa)[colnames(Goa) == "Place_to_Visit[1:10]"] <- "Data_Type"
colnames(Goa)[colnames(Goa) == "url_img[1:10]"] <- "Picture_URL"
Goa
```

## Madhya Pradesh
```{r}
#| echo: FALSE
#| eval: TRUE
# Madhya_Pradesh

##### for url of photo...............

html_Madhya_Pradesh <- read_html("https://en.wikipedia.org/wiki/Tourism_in_Madhya_Pradesh")

html_Madhya_Pradesh1 <- html_Madhya_Pradesh%>%html_elements(".mw-file-element")%>%html_attr("src")

html_Madhya_Pradesh1 <- html_Madhya_Pradesh1[2:11]

url_img <- c()
for(i in 1:10)
{
  
  url_img[i] <- paste0("https:",html_Madhya_Pradesh1[i])
}

###### for name of photo..............

html_Madhya_Pradesh2 <- html_Madhya_Pradesh%>%html_elements(".mw-default-size")%>%html_text()

html_Madhya_Pradesh2[10] <- "Tal_ul_Masjid, Bhopal"

html_Madhya_Pradesh2 <- html_Madhya_Pradesh2[1:10] 
Place_to_Visit <-  html_Madhya_Pradesh2

Madhya_Pradesh <- data.frame(Place_to_Visit,url_img)

Madhya_Pradesh <- tibble(Place_to_Visit[1:10],url_img[1:10])
colnames(Madhya_Pradesh)[colnames(Madhya_Pradesh) == "Place_to_Visit[1:10]"] <- "Data_Type"
colnames(Madhya_Pradesh)[colnames(Madhya_Pradesh) == "url_img[1:10]"] <- "Picture_URL"
Madhya_Pradesh
```

## Assam
```{r}
#| echo: FALSE
#| eval: TRUE
# Assam

##### for url of photo...............

html_Assam <- read_html("https://en.wikipedia.org/wiki/Tourism_in_Assam")

html_Assam1 <- html_Assam%>%html_elements(".mw-file-element")%>%html_attr("src")

html_Assam1 <- html_Assam1[3:9]
url_img <- c()
for(i in 1:7)
{
  
  url_img[i] <- paste0("https:",html_Assam1[i])
}

###### for name of photo..............

html_Assam2 <- html_Assam%>%html_elements(".mw-halign-right")%>%html_text()

html_Assam2[4] <- "Kamakhya Temple"
html_Assam2[5] <- "Majuli island"
html_Assam2[6] <- "Nameri national Park"
html_Assam2[7] <- "Rang ghar pavilions"

Place_to_Visit <- html_Assam2

Assam <- data.frame(Place_to_Visit,url_img)

Assam <- tibble(Place_to_Visit[1:7],url_img[1:7])
colnames(Assam)[colnames(Assam) == "Place_to_Visit[1:7]"] <- "Data_Type"
colnames(Assam)[colnames(Assam) == "url_img[1:7]"] <- "Picture_URL"
Assam
```

## West Bengal
```{r}
#| echo: FALSE
#| eval: TRUE
# 1.Tourism in West Bengal....//


html_West_Bengal<-read_html("https://en.wikipedia.org/wiki/Tourism_in_West_Bengal")

html_West_Bengal1 <- html_West_Bengal%>%html_elements(".mw-file-element")%>%html_attr("src")
html_West_Bengal1 <- html_West_Bengal1[1:10]
url_img <- c()
for(i in 1:10)
{
  
  url_img[i] <- paste0("https:",html_West_Bengal1[i])
}

# for name of photo..............

html_West_Bengal2 <- html_West_Bengal%>%html_elements(".mw-halign-right")%>%html_text()
html_West_Bengal2[1]= "Darjeeling Himalayan Railway"
html_West_Bengal2[2]= "Howrah Bridge"
html_West_Bengal2[3]= "Acharya Jagadish Chandra Bose Indian Botanic Garden"
html_West_Bengal2[4]= "Morgan House Kalimpong"
html_West_Bengal2[5]= "Mandarmani Sea Beach"
html_West_Bengal2[6]= "Chintamani Kar Bird Sanactuary Kolkata"
html_West_Bengal2[7]= "Panthera tigris tigris"
html_West_Bengal2[8]= "Gorumara National Park Panorama"
html_West_Bengal2[9]= "baul singers"
html_West_Bengal2[10]= "Sunderban"
Place_to_Visit <- html_West_Bengal2[1:10]

West_bengal <- data.frame(Place_to_Visit,url_img)
West_bengal <- tibble(Place_to_Visit[1:10],url_img[1:10])
colnames(West_bengal)[colnames(West_bengal) == "Place_to_Visit[1:10]"] <- "Data_Type"
colnames(West_bengal)[colnames(West_bengal) == "url_img[1:10]"] <-"Picture_URL"
West_bengal
```

## Delhi
```{r}
#| echo: FALSE
#| eval: TRUE
html_Delhi<-read_html("https://en.wikipedia.org/wiki/List_of_tourist_attractions_in_Delhi")
html_Delhi1 <- html_Delhi%>%html_elements(".mw-file-element")%>%html_attr("src")
html_Delhi1 <- html_Delhi1[5:14]

url_img <- c()
for(i in 1:10)
{
  
  url_img[i] <- paste0("https:",html_Delhi1[i])
}


# for name of photo..............

html_Delhi2 <- html_Delhi%>%html_elements("mw-default-size")%>%html_text()
html_Delhi2[1]= "Rashtrapati_Bhavan"
html_Delhi2[2]= "Qutub minar"
html_Delhi2[3]= "Red Fort"
html_Delhi2[4]= "Akshardham Temple"
html_Delhi2[5]= "ISKCON Temple"
html_Delhi2[6]= "Digambar Jain Lal Mandir"
html_Delhi2[7]= "Gurudwara Bangla Sahib"
html_Delhi2[8]= "Jama Masjid"
html_Delhi2[9]= "Cathedral Church"
html_Delhi2[10]= "National War Memorial"
Place_to_Visit <- html_Delhi2[1:10]

Delhi <- data.frame(Place_to_Visit,url_img)

Delhi <- tibble(Place_to_Visit[1:10],url_img[1:10])
colnames(Delhi)[colnames(Delhi) == "Place_to_Visit[1:10]"] <- "Data_Type"
colnames(Delhi)[colnames(Delhi) == "url_img[1:10]"] <-"Picture_URL"
Delhi
```

## Telangana
```{r}
#| echo: FALSE
#| eval: TRUE
# 3.Tourism of Telangana

html_Telangana<-read_html("https://en.wikipedia.org/wiki/Tourism_in_Telangana")
html_Telangana1 <- html_Telangana%>%html_elements(".mw-file-element")%>%html_attr("src")
html_Telangana1 <- html_Telangana1[1:8]

url_img <- c()
for(i in 1:8)
{
  
  url_img[i] <- paste0("https:",html_Telangana1[i])
}


# for name of photo..............

html_Telangana2 <- html_Telangana%>%html_elements("mw-default-size")%>%html_text()
html_Telangana2[1]= "Charminar"
html_Telangana2[2]= "Warangal fort"
html_Telangana2[3]= "Bhongir Fort"
html_Telangana2[4]= "Jain temple warangal"
html_Telangana2[5]= "Bhadrachalam Temple"
html_Telangana2[6]= "Birla Temple"
html_Telangana2[7]= "Mecca Masjid"
html_Telangana2[8]= "Medak Cathedral"
Place_to_Visit <- html_Telangana2[1:8]

Telangana <- data.frame(Place_to_Visit,url_img)
Telangana <- data.frame(Place_to_Visit,url_img)
Telangana <- tibble(Place_to_Visit[1:8],url_img[1:8])
colnames(Telangana)[colnames(Telangana) == "Place_to_Visit[1:8]"] <- "Data_Type"
colnames(Telangana)[colnames(Telangana) == "url_img[1:8]"] <-"Picture_URL"
Telangana
```

## Uttrakhand
```{r}
#| echo: FALSE
#| eval: TRUE
# 4.Tourism in Uttrakhand

html_Uttrakhand<-read_html("https://en.wikipedia.org/wiki/Tourism_in_Uttarakhand")
html_Uttrakhand1 <- html_Uttrakhand%>%html_elements(".mw-file-element")%>%html_attr("src")
html_Uttrakhand1 <- html_Uttrakhand1[1:10]

url_img <- c()
for(i in 1:10)
{
  
  url_img[i] <- paste0("https:",html_Uttrakhand1[i])
}

# for name of photo..............

html_Uttrakhand2 <- html_Uttrakhand%>%html_elements("mw-default-size")%>%html_text()
html_Uttrakhand2[1]= "Badrinath Valley"
html_Uttrakhand2[2]= "Kedarnath"
html_Uttrakhand2[3]= "Gangotri temple"
html_Uttrakhand2[4]= "Yamunotri temple and ashram"
html_Uttrakhand2[5]= "Kedarnath Temple"
html_Uttrakhand2[6]= "Tungnath temple"
html_Uttrakhand2[7]= "Rudranath temple"
html_Uttrakhand2[8]= "Madhyamaheshwar Temple"
html_Uttrakhand2[9]= "Kalpehswar"
html_Uttrakhand2[10]= "Nainital lake"
Place_to_Visit <- html_Uttrakhand2[1:10]
Uttrakhand <- data.frame(Place_to_Visit,url_img)
Uttrakhand <- tibble(Place_to_Visit[1:10],url_img[1:10])
colnames(Uttrakhand)[colnames(Uttrakhand) == "Place_to_Visit[1:10]"] <- "Data_Type"
colnames(Uttrakhand)[colnames(Uttrakhand) == "url_img[1:10]"] <-"Picture_URL"
Uttrakhand
```

## TamilNadu
```{r}
#| echo: FALSE
#| eval: TRUE
# 5.Tourism in Tamilnadu

html_Tamilnadu<-read_html("https://en.wikipedia.org/wiki/Tourism_in_Tamil_Nadu")
html_Tamilnadu1 <- html_Tamilnadu%>%html_elements(".mw-file-element")%>%html_attr("src")
html_Tamilnadu1 <- html_Tamilnadu1[2:11]

url_img <- c()
for(i in 1:10)
{
  
  url_img[i] <- paste0("https:",html_Tamilnadu1[i])
}

# for name of photo..............

html_Tamilnadu2 <- html_Tamilnadu%>%html_elements("mw-default-size")%>%html_text()
html_Tamilnadu2[1]= "Marina Beach"
html_Tamilnadu2[2]= "Tamil Nadu Flag"
html_Tamilnadu2[3]= "south of Chenna"
html_Tamilnadu2[4]= "Madurai Meenakshi"
html_Tamilnadu2[5]= "Gangaikonda Cholapuram Temple Gopuram"
html_Tamilnadu2[6]= "Thiruvannamalai Annamalaiyar Temple"
html_Tamilnadu2[7]= "Hogenakkal Falls bathing area"
html_Tamilnadu2[8]= "Parisal Boating in Hogenakkal falls"
html_Tamilnadu2[9]= "Pichavaram Mangrove Forest"
html_Tamilnadu2[10]= "Amman Temple"
Place_to_Visit <- html_Tamilnadu2[1:10]

TamilNadu <- data.frame(Place_to_Visit,url_img)
TamilNadu <- data.frame(Place_to_Visit,url_img)
TamilNadu <- tibble(Place_to_Visit[1:10],url_img[1:10])
colnames(TamilNadu)[colnames(TamilNadu) == "Place_to_Visit[1:10]"] <- "Data_Type"
colnames(TamilNadu)[colnames(TamilNadu) == "url_img[1:10]"] <-"Picture_URL"
TamilNadu
```

## Kerala
```{r}
#| echo: FALSE
#| eval: TRUE
# 6.Tourism in Kerala

html_Kerala<-read_html("https://en.wikipedia.org/wiki/Tourism_in_Kerala")
html_Kerala1 <- html_Kerala%>%html_elements(".mw-file-element")%>%html_attr("src")
html_Kerala1 <- html_Kerala1[3:12]

url_img <- c()
for(i in 1:10)
{
  
  url_img[i] <- paste0("https:",html_Kerala1[i])
}
# for name of photo..............

html_Kerala2 <- html_Kerala%>%html_elements("mw-default-size")%>%html_text()
html_Kerala2[1]= "House Boat"
html_Kerala2[2]= "Light house in Ponnani"
html_Kerala2[3]= "Resort calicut kerala"
html_Kerala2[4]= "Kerala Houseboat"
html_Kerala2[5]= "Kottappura nileshwaram house"
html_Kerala2[6]= "Munnar Hillscape"
html_Kerala2[7]= "Sithar Kundu View Point"
html_Kerala2[8]= "Lightmatter lion tailed macaque"
html_Kerala2[9]= "The View of the Athirapally Falls during the onset of Monsoon"
html_Kerala2[10]= "Sea From Bakel"
Place_to_Visit <- html_Kerala2[1:10]
Kerala <- data.frame(Place_to_Visit,url_img)

Kerala <- tibble(Place_to_Visit[1:10],url_img[1:10])
colnames(Kerala)[colnames(Kerala) == "Place_to_Visit[1:10]"] <- "Data_Type"
colnames(Kerala)[colnames(Kerala) == "url_img[1:10]"] <-"Picture_URL"
Kerala
```

## Rajasthan
```{r}
#| echo: FALSE
#| eval: TRUE
# 7.Tourism in Rajasthan

html_Rajasthan<-read_html("https://en.wikipedia.org/wiki/Tourism_in_Rajasthan")
html_Rajasthan1 <- html_Rajasthan%>%html_elements(".mw-file-element")%>%html_attr("src")
html_Rajasthan1 <- html_Rajasthan1[2:11]

url_img <- c()
for(i in 1:10)
{
  
  url_img[i] <- paste0("https:",html_Rajasthan1[i])
}


# for name of photo..............

html_Rajasthan2 <- html_Rajasthan%>%html_elements("mw-default-size")%>%html_text()
html_Rajasthan2[1]= "Udaipur Lake Palace"
html_Rajasthan2[2]= "Hawa Mahal on a stormy afternoon"
html_Rajasthan2[3]= "JagMandir"
html_Rajasthan2[4]= "City Palace by lake Pichola"
html_Rajasthan2[5]= "Mehrangarh Fort"
html_Rajasthan2[6]= "AmberFort"
html_Rajasthan2[7]= "Amer Fort"
html_Rajasthan2[8]= "Jaisalmer forteresse"
html_Rajasthan2[9]= "Ancient Temples Jaisalmer"
html_Rajasthan2[10]= "Walls of Kumbhalgarh"  
Place_to_Visit <- html_Rajasthan2[1:10]

Rajasthan <- data.frame(Place_to_Visit,url_img)
Rajasthan <- tibble(Place_to_Visit[1:10],url_img[1:10])
colnames(Rajasthan)[colnames(Rajasthan) == "Place_to_Visit[1:10]"] <- "Data_Type"
colnames(Rajasthan)[colnames(Rajasthan) == "url_img[1:10]"] <-"Picture_URL"
Rajasthan
```

## Odisha
```{r}
#| echo: FALSE
#| eval: TRUE
# 8.Tourism in Odisha
html_Odisha<-read_html("https://en.wikipedia.org/wiki/Tourism_in_Odisha")
html_Odisha1 <- html_Odisha%>%html_elements(".mw-file-element")%>%html_attr("src")
html_Odisha1 <- html_Odisha1[3:12]

url_img <- c()
for(i in 1:10)
{
  
  url_img[i] <- paste0("https:",html_Odisha1[i])
}
# for name of photo..............


html_Odisha2 <- html_Odisha%>%html_elements("mw-default-size")%>%html_text()
html_Odisha2[1]= "Konarak Sun Temple"
html_Odisha2[2]= "Brahmeswar Temple Bhubaneswar"
html_Odisha2[3]= "Mukteswar temple"
html_Odisha2[4]= "Lingaraj temple"
html_Odisha2[5]= "Rajarani Temple"
html_Odisha2[6]= "Chilika Lake"
html_Odisha2[7]= "Barehipani Falls"
html_Odisha2[8]= "Badaghagara Kendujhar"
html_Odisha2[9]= "Khandhadhar Falls"
html_Odisha2[10]= "Sanaghagara Kendujhar"
Place_to_Visit <- html_Odisha2[1:10]
Odisha <- data.frame(Place_to_Visit,url_img)
Odisha <- tibble(Place_to_Visit[1:10],url_img[1:10])
colnames(Odisha)[colnames(Odisha) == "Place_to_Visit[1:10]"] <- "Data_Type"
colnames(Odisha)[colnames(Odisha) == "url_img[1:10]"] <-"Picture_URL"
Odisha
```

## Maharastra
```{r}
#| echo: FALSE
#| eval: TRUE
# 9.Tourism in Maharastra
html_Maharastra<-read_html("https://en.wikipedia.org/wiki/Tourism_in_Maharashtra")
html_Maharastra1 <- html_Maharastra%>%html_elements(".mw-file-element")%>%html_attr("src")
html_Maharastra1 <- html_Maharastra1[4:13]

url_img <- c()
for(i in 1:10)
{
  
  url_img[i] <- paste0("https:",html_Maharastra1[i])
}


# for name of photo..............


html_Maharastra2 <- html_Maharastra%>%html_elements("mw-default-size")%>%html_text()
html_Maharastra2[1]= "Sydney point panchghani"
html_Maharastra2[2]= "Pandharpur Aashad panoramio"
html_Maharastra2[3]= "Sri Hazur Sahib Nanded"
html_Maharastra2[4]= "Statue Of Ahimsa MangiTungi"
html_Maharastra2[5]= "Bahubali Kumbhoj"
html_Maharastra2[6]= "Kailasha temple at ellora"
html_Maharastra2[7]= "Elephanta Caves"
html_Maharastra2[8]= "Ajanta"
html_Maharastra2[9]= "Pataleshwar Caves temple"
html_Maharastra2[10]= "Bibika"
Place_to_Visit <- html_Maharastra2[1:10]
Maharastra <- data.frame(Place_to_Visit,url_img)
Maharastra <- data.frame(Place_to_Visit,url_img)
Maharastra <- tibble(Place_to_Visit[1:10],url_img[1:10])
colnames(Maharastra)[colnames(Maharastra) == "Place_to_Visit[1:10]"] <- "Data_Type"
colnames(Maharastra)[colnames(Maharastra) == "url_img[1:10]"] <-"Picture_URL"
Maharastra
```

## Andaman & Nicobar
```{r}
#| echo: FALSE
#| eval: TRUE
# 10.Tourism in  Andaman and Nicobar
html_Andaman_and_Nicobar <- read_html("https://en.wikipedia.org/wiki/Tourism_in_the_Andaman_and_Nicobar_Islands")
html_Andaman_and_Nicobar1 <- html_Andaman_and_Nicobar%>%html_elements(".mw-file-element")%>%html_attr("src")
html_Andaman_and_Nicobar1 <- html_Andaman_and_Nicobar1[1:6] 

url_img <- c()
for(i in 1:6)
{
  
  url_img[i] <- paste0("https:",html_Andaman_and_Nicobar1[i])
}

# for photo name........//

html_Andaman_and_Nicobar2 <- html_Andaman_and_Nicobar%>%html_elements(".mw-default-size")%>%html_text() 
html_Andaman_and_Nicobar2[1]= "CellularJail Wings" 
html_Andaman_and_Nicobar2[2]= "Gallows on Viper Island" 
html_Andaman_and_Nicobar2[3]= "Havelock Island"
html_Andaman_and_Nicobar2[4]= "India Tourism Elephant"
html_Andaman_and_Nicobar2[5]= "Viper Island" 
html_Andaman_and_Nicobar2[6]= "Andaman ross"

Place_to_Visit <- html_Andaman_and_Nicobar2[1:6] 
Andaman_and_Nicobar <- data.frame(Place_to_Visit,url_img)
Andaman_and_Nicobar <- tibble(Place_to_Visit[1:6],url_img[1:6])
colnames(Andaman_and_Nicobar)[colnames(Andaman_and_Nicobar) == "Place_to_Visit[1:6]"] <- "Data_Type"
colnames(Andaman_and_Nicobar)[colnames(Andaman_and_Nicobar) == "url_img[1:6]"] <-"Picture_URL"
Andaman_and_Nicobar
```


# Motorbike Tour

The "Motorbike Tour" tab offers information about motorcycle tours in India.

We scrapped data nearly 20 places to visit by motorbike from "https://www.thrillophilia.com/motorcycle-tours-in-india".

Make a table named my_tibble which contains columns as :-

Tour

Description

Common Route Taken

Total Riding distance

Best Riding Season

## Data Extraction and Preprocessing

```{r}
#| echo: FALSE
#| eval: TRUE
url <- read_html("https://www.thrillophilia.com/motorcycle-tours-in-india")
data3 <- url %>% html_elements(".h3") %>% html_text2()
data3 <- data3[1:20]

data4 <- url %>% html_elements(".text-holder.read-more-wrap") %>% html_text2()

```

```{r}
#| echo: FALSE
#| eval: TRUE
a <- c()
b <- c()
c <- c()
d <- c()
e <- c()

a <- strsplit(x = data4[1],split = "Route Map:")
b <- strsplit(a[[1]][2],split = "Total Riding Distance:")
c <- strsplit(b[[1]][2],split = "Best Riding Season:")
d <- strsplit(c[[1]][2],split = "Also")
e1 <- data_frame(a[[1]][1],b[[1]][1],c[[1]][1],d[[1]][1])

my_tibble <- e1

a <- strsplit(x = data4[2],split = "Route Map:")
b <- strsplit(a[[1]][2],split = "Total Riding Distance:")
c <- strsplit(b[[1]][2],split = "Best Riding Season:")
d <- strsplit(c[[1]][2],split = "Also")
e2 <- data_frame(a[[1]][1],b[[1]][1],c[[1]][1],d[[1]][1])

my_tibble <- add_row(my_tibble,e2)



a <- strsplit(x = data4[3],split ="Common route taken:")
b <- strsplit(a[[1]][2],split = "Total Riding Distance:")
c <- strsplit(b[[1]][2],split = "Best Riding Season:")
d <- strsplit(c[[1]][2],split = "Also")
e3 <- data_frame(a[[1]][1],b[[1]][1],c[[1]][1],d[[1]][1])

my_tibble <- add_row(my_tibble,e3)

a <- strsplit(x = data4[4],split ="Route Map:")
b <- strsplit(a[[1]][2],split = "Total Riding Distance:")
c <- strsplit(b[[1]][2],split = "Best Riding Season:")
d <- strsplit(c[[1]][2],split = "Also")
e4 <- data_frame(a[[1]][1],b[[1]][1],c[[1]][1],d[[1]][1])

my_tibble <- add_row(my_tibble,e4)

a <- strsplit(x = data4[5],split ="Route Map:")
b <- strsplit(a[[1]][2],split = "Total Riding Distance:")
c <- strsplit(b[[1]][2],split = "Best Riding Season:")
d <- strsplit(c[[1]][2],split = "Also")
e5 <- data_frame(a[[1]][1],b[[1]][1],c[[1]][1],d[[1]][1])

my_tibble <- add_row(my_tibble,e5)

a <- strsplit(x = data4[6],split ="Route Map:")
b <- strsplit(a[[1]][2],split = "Total Riding Distance:")
c <- strsplit(b[[1]][2],split = "Best Riding Season:")
d <- strsplit(c[[1]][2],split = "Also")
e6 <- data_frame(a[[1]][1],b[[1]][1],c[[1]][1],d[[1]][1])

my_tibble <- add_row(my_tibble,e6)

a <- strsplit(x = data4[7],split ="Common Route Taken:")
b <- strsplit(a[[1]][2],split = "Total Riding Distance:")
c <- strsplit(b[[1]][2],split = "Best Riding Season:")
d <- strsplit(c[[1]][2],split = "Also")
e7 <- data_frame(a[[1]][1],b[[1]][1],c[[1]][1],d[[1]][1])

my_tibble <- add_row(my_tibble,e7)

a <- strsplit(x = data4[8],split ="Common Route Taken:")
b <- strsplit(a[[1]][2],split = "Total Riding Distance:")
c <- strsplit(b[[1]][2],split = "Best Riding Season:")
d <- strsplit(c[[1]][2],split = "Also")
e8 <- data_frame(a[[1]][1],b[[1]][1],c[[1]][1],d[[1]][1])

my_tibble <- add_row(my_tibble,e8)

a <- strsplit(x = data4[9],split ="Common Route Taken:")
b <- strsplit(a[[1]][2],split = "Total Riding Distance:")
c <- strsplit(b[[1]][2],split = "Best Riding Season:")
d <- strsplit(c[[1]][2],split = "Also")
e9 <- data_frame(a[[1]][1],b[[1]][1],c[[1]][1],d[[1]][1])

my_tibble <- add_row(my_tibble,e9)

a <- strsplit(x = data4[10],split ="Common Route Taken:")
b <- strsplit(a[[1]][2],split = "Total Riding Distance:")
c <- strsplit(b[[1]][2],split = "Best Riding Season:")
d <- strsplit(c[[1]][2],split = "Also")
e10 <- data_frame(a[[1]][1],b[[1]][1],c[[1]][1],d[[1]][1])

my_tibble <- add_row(my_tibble,e10)

a <- strsplit(x = data4[11],split ="Common Route Taken:")
b <- strsplit(a[[1]][2],split = "Total Riding Distance:")
c <- strsplit(b[[1]][2],split = "Best Riding Season:")
d <- strsplit(c[[1]][2],split = "Also")
e11 <-data_frame(a[[1]][1],b[[1]][1],c[[1]][1],d[[1]][1])

my_tibble <- add_row(my_tibble,e11)

a <- strsplit(x = data4[12],split ="Common Route Taken:")
b <- strsplit(a[[1]][2],split = "Total Riding Distance:")
c <- strsplit(b[[1]][2],split = "Best Riding Season:")
d <- strsplit(c[[1]][2],split = "Also")
e12 <- data_frame(a[[1]][1],b[[1]][1],c[[1]][1],d[[1]][1])

my_tibble <- add_row(my_tibble,e12)

a <- strsplit(x = data4[13],split ="Common Route Taken:")
b <- strsplit(a[[1]][2],split = "Total Riding Distance:")
c <- strsplit(b[[1]][2],split = "Best Riding Season:")
d <- strsplit(c[[1]][2],split = "Also")
e13 <- data_frame(a[[1]][1],b[[1]][1],c[[1]][1],d[[1]][1])

my_tibble <- add_row(my_tibble,e13)

a <- strsplit(x = data4[14],split ="Common Route Taken:")
b <- strsplit(a[[1]][2],split = "Total Riding Distance:")
c <- strsplit(b[[1]][2],split = "Best Riding Season:")
d <- strsplit(c[[1]][2],split = "Also")
e14 <- data_frame(a[[1]][1],b[[1]][1],c[[1]][1],d[[1]][1])

my_tibble <- add_row(my_tibble,e14)

a <- strsplit(x = data4[15],split ="Common Route Taken:")
b <- strsplit(a[[1]][2],split = "Total Riding Distance:")
c <- strsplit(b[[1]][2],split = "Best Riding Season:")
d <- strsplit(c[[1]][2],split = "Also")
e15 <- data_frame(a[[1]][1],b[[1]][1],c[[1]][1],d[[1]][1])

my_tibble <- add_row(my_tibble,e15)

a <- strsplit(x = data4[16],split ="Common Route Taken:")
b <- strsplit(a[[1]][2],split = "Total Riding Distance:")
c <- strsplit(b[[1]][2],split = "Best Riding Season:")
d <- strsplit(c[[1]][2],split = "Also")
e16 <- data_frame(a[[1]][1],b[[1]][1],c[[1]][1],d[[1]][1])

my_tibble <- add_row(my_tibble,e16)

a <- strsplit(x = data4[17],split ="Common Route Taken:")
b <- strsplit(a[[1]][2],split = "Total Riding Distance:")
c <- strsplit(b[[1]][2],split = "Best Riding Season:")
d <- strsplit(c[[1]][2],split = "Also")
e17 <- data_frame(a[[1]][1],b[[1]][1],c[[1]][1],d[[1]][1])

my_tibble <- add_row(my_tibble,e17)

a <- strsplit(x = data4[18],split ="Common Route Taken:")
b <- strsplit(a[[1]][2],split = "Total Riding Distance:")
c <- strsplit(b[[1]][2],split = "Best Riding Season:")
d <- strsplit(c[[1]][2],split = "Also")
e18 <- data_frame(a[[1]][1],b[[1]][1],c[[1]][1],d[[1]][1])

my_tibble <- add_row(my_tibble,e18)

a <- strsplit(x = data4[19],split ="Common Route Taken:")
b <- strsplit(a[[1]][2],split = "Total Riding Distance:")
c <- strsplit(b[[1]][2],split = "Best Riding Season:")
d <- strsplit(c[[1]][2],split = "Also")
e19 <- data_frame(a[[1]][1],b[[1]][1],c[[1]][1],d[[1]][1])

my_tibble <- add_row(my_tibble,e19)

a <- strsplit(x = data4[20],split ="Common Route Taken:")
b <- strsplit(a[[1]][2],split = "Total Riding Distance:")
c <- strsplit(b[[1]][2],split = "Best Riding Season:")
d <- strsplit(c[[1]][2],split = "Also")
e20 <- data_frame(a[[1]][1],b[[1]][1],c[[1]][1],d[[1]][1])

my_tibble <- add_row(my_tibble,e20)

my_tibble <- my_tibble %>%
  mutate(data3) %>%
  select(data3, everything())

colnames(my_tibble)[colnames(my_tibble) == "data3"] <- "Tour"
colnames(my_tibble)[colnames(my_tibble) == "a[[1]][1]"] <- "Description"
colnames(my_tibble)[colnames(my_tibble) == "b[[1]][1]"] <- "Common Route Taken"
colnames(my_tibble)[colnames(my_tibble) == "c[[1]][1]"] <- "Total Riding Distance"
colnames(my_tibble)[colnames(my_tibble) == "d[[1]][1]"] <- "Best Riding Season"
my_tibble

```



# Travel Monthwise

In the "Travel Monthwise" tab, users can select a specific month to get travel information.

We extraced data from "https://www.tourism-of-india.com/travel-by-month.html".



## Data Extraction, Preprocessing Display

```{r}
#| echo: FALSE
#| eval: TRUE
month <- read_html("https://www.tourism-of-india.com/travel-by-month.html")

#data1 <- html %>% html_elements(".mt-0") %>% html_text2()
#data1

data_month <- month %>% html_elements(".text") %>% html_text2()


paragraph <- c()
words <- c()
first_three_words <- c()
remaining_text <- c()
for(i in 1:length(data_month))
{
  paragraph[i] <- gsub("\n\n",x = data_month[i],replacement = " ")
  # Split the paragraph into words
  words <- unlist(strsplit(paragraph[i], " "))
  
  # Extract the first three words
  first_three_words[i] <- paste(words[1:1], collapse = " ")
  
  # Remaining paragraph
  remaining_text[i] <- paste(words[4:length(words)], collapse = " ")
  
}

Travel_by_Month_in_India <- tibble(first_three_words,remaining_text)
colnames(Travel_by_Month_in_India) <- c("Months","Description")
Travel_by_Month_in_India

```


```{r}
#| echo: FALSE
#| eval: TRUE
State_list <- c("Andhra_Pradesh",
                "Bihar",
                "chattisgarh",
                "Gujarat",
                "Uttar_pradesh",
                "Karnataka",
                "Jharkhand",
                "Goa",
                " Madhya_Pradesh",
                "Assam",
                "West_bengal",
                "Delhi",
                "Telangana",
                "Uttrakhand",
                "TamilNadu",
                "Kerala",
                "Rajasthan",
                "Odisha",
                "Maharastra",
                "Andaman_and_Nicobar",
                "Jammu_and_kashmir",
                "Meghalaya",
                "Sikkim",
                "Nagaland",
                "Tripura",
                "Mizoram",
                "Himachal_Pradesh",
                "Haryana",
                "Panjab",
                "Manipur",
                "Chandigarh",
                "Dadra_and_Nagar_Haveli",
                "Ladakh",
                "Lakshadeep",
                "Puducherry"
                )
# Define your data tables (table_1, table_2, etc.) and table_list here
# Sample data for table2_list 
table2_list <- c("North_India",
                 "South_India",
                 "Central_India",
                 "West_India",
                 "East_India",
                 "NorthEast_India")
table_list <- c(
                "Foreign tourist arrivals in India (1997–2022).",
                "Foreign exchange earnings from tourism in India (1997–2020).",
                "Source countries for foreign tourist arrivals in India in 2019.",
                "Share of top 10 states/UTs of India in number of foreign tourist visits in 2017.",
                "Share of top 10 states/UTs of India in number of domestic tourist visits in 2017.",
                "Scrapped_data_table")

```


# User Interface and Interaction

The Shiny app provides a user-friendly interface with interactive elements, including dropdown menus and data tables. Users can interact with the app to select the data they want to explore.

### Shiny App Code

```{r}

ui <- fluidPage(
  tabsetPanel(
    tabPanel("Tables",
             titlePanel("Table and Graph"),
             sidebarLayout(
               sidebarPanel(
                 selectInput("tableType", "Select Table Type:", choices = table_list),
               ),
               mainPanel(
                 DTOutput("table"),
                 plotOutput("plot")
               )
             )),
    tabPanel("Main parts of India",
             titlePanel("Part Wise Tourist Place"),
             
             sidebarLayout(
               sidebarPanel(
                 selectInput("N_S", "Select", choices = table2_list),
                 
                 uiOutput("data_type"),
                 uiOutput("pictures")
               ),
               
               mainPanel(
                 DTOutput("content")
               )
             )
             ),
    tabPanel("States",
             tabPanel("States",
                      titlePanel("State Wise Tourist Place"),
                      
                      sidebarLayout(
                        sidebarPanel(
                          selectInput("rajya", "State/Union Territory", choices = State_list),
                          
                          uiOutput("data_type3"),
                          uiOutput("pictures3")
                        ),
                        
                        mainPanel(
                          DTOutput("content3")
                        )
                      )
             )),
    tabPanel("Motorbike Tour",
             titlePanel("Bike Tour Table"),
             mainPanel(
               DTOutput("myTable")
             )),
    tabPanel("Travel Monthwise",
             titlePanel("Travel by Month in India"),
             sidebarLayout(
               sidebarPanel(
                 selectInput("Month", "Select Month:", choices = Travel_by_Month_in_India$Months),
               ),
               mainPanel(
                 textOutput("Description")
               )
             ))
  )
)

server <- function(input, output) {
  datasetInput1 <- reactive({
    switch(input$tableType,
           "Foreign tourist arrivals in India (1997–2022)." = table_1,
           "Foreign exchange earnings from tourism in India (1997–2020)." = table_2,
           "Source countries for foreign tourist arrivals in India in 2019." = table_3,
           "Share of top 10 states/UTs of India in number of foreign tourist visits in 2017." = table_4,
           "Share of top 10 states/UTs of India in number of domestic tourist visits in 2017." = table_5,
           "Scrapped_data_table" = final_table
    )
  })
  
  output$table <- renderDT({
    datatable(
      datasetInput1(),
      escape = FALSE
    )
   
  })
  
  output$plot <- renderPlot({
    data <- datasetInput1()
    
    if (identical(data, table_1)) {
      ggplot(data = data) +
        geom_line(mapping = aes(x = Year, y = `Arrivals (millions)`), linetype = 1, linewidth = 1, color = "red")
    } else if (identical(data, table_2)) {

      
      
      # Assuming your data is in a tibble named table_2
      data$`Earnings (₹ crores)` <- as.numeric(gsub(",", "", gsub("−", "-", data$`Earnings (₹ crores)`)))
      # Create a bar plot
      barplot(data$`Earnings (₹ crores)`, names.arg = data$Year, col = "blue", main = "Earnings Over the Years",
              xlab = "Year", ylab = "Earnings in ₹ Crores")
      
    } else if (identical(data, table_3)) {
      
      data <- data[-c(12),]
      
      # Assuming your data is in a tibble named table_2
      data$Number <- as.numeric(gsub(",", "", data$Number))
      barplot(data$Number, names.arg = data$Country, col = "blue", main = "Number of People",
              xlab = "Country", ylab = "Number")
      
    } else if (identical(data, table_4)) {
      
      data <- data[c(1:10),]
      
      # Assuming your data is in a tibble named table_2
      data$Number <- as.numeric(gsub(",", "", data$Number))
      barplot(data$Number, names.arg = data$`State/Union Territory`, col = "blue", main = "Share of top 10 states/UTs of India in number of foreign tourist visits in 2017",
              xlab = "State/Union Territory", ylab = "NUmber")
      
    } else if (identical(data, table_5)) {
      
      data <- data[c(1:10),]
      
      # Assuming your data is in a tibble named table_2
      data$Number <- as.numeric(gsub(",", "", data$Number))
      barplot(data$Number, names.arg = data$`State/Union Territory`, col = "blue", main = "Share of top 10 states/UTs of India in number of domestic tourist visits in 2017",
              xlab = "State/Union Territory", ylab = "NUmber")
      
    } 
  })
  
  datasetInput <- reactive({
    switch(input$N_S,
           "North_India" = North_India,
           "South_India" = South_India,
           "Central_India" = Central_India,
           "West_India" = West_India,
           "East_India" = East_India,
           "NorthEast_India" = NorthEast_India
    )
  })
  
  output$data_type <- renderUI({
    data <- datasetInput()
    selectInput("data_type", "Please Select", choices = data$Data_Type)
  })
  
  output$pictures <- renderUI({
    data <- datasetInput()
    pictures_url <- data[data$Data_Type == input$data_type, "Picture_URL"]
    
    if (is.null(pictures_url) || length(pictures_url) == 0) {
      return(NULL)
    }
    
    pictures <- lapply(pictures_url, function(url) {
      tags$img(src = url)
    })
    
    div(pictures)
  })
  
  output$content <- renderDT({
    data <- datasetInput()
    datatable(data)
  })
  
  output$Description <- renderText({
    if (input$Month == "November")
    {
      Travel_by_Month_in_India$Description[1]
    } else if (input$Month == "December")
    {
      Travel_by_Month_in_India$Description[2]
    } else if (input$Month == "January")
    {
      Travel_by_Month_in_India$Description[3]
    } else if (input$Month == "February")
    {
      Travel_by_Month_in_India$Description[4]
    } else if (input$Month == "February")
    {
      Travel_by_Month_in_India$Description[4]
    } else if (input$Month == "March")
    {
      Travel_by_Month_in_India$Description[5]
    } else if (input$Month == "April")
    {
      Travel_by_Month_in_India$Description[6]
    } else if (input$Month == "May")
    {
      Travel_by_Month_in_India$Description[7]
    } else if (input$Month == "June")
    {
      Travel_by_Month_in_India$Description[8]
    } else if (input$Month == "July")
    {
      Travel_by_Month_in_India$Description[9]
    } else if (input$Month == "August")
    {
      Travel_by_Month_in_India$Description[10]
    } else if (input$Month == "September")
    {
      Travel_by_Month_in_India$Description[11]
    } else if (input$Month == "October")
    {
      Travel_by_Month_in_India$Description[12]
    } 
  })
  
  output$myTable <- renderDT({
    datatable(my_tibble)
  })
  
  datasetInput3 <- reactive({
    switch(input$rajya,
           "Andhra_Pradesh" = Andhra_Pradesh,
           "Bihar" = Bihar,
           "chattisgarh" = chattisgarh,
           "Gujarat" = Gujarat,
           "Uttar_pradesh" = Uttar_pradesh,
           "Karnataka" = Karnataka,
           "Jharkhand" = Jharkhand,
           "Goa" = Goa,
           "Madhya_Pradesh" = Madhya_Pradesh,
           "Assam" = Assam,
           "West_bengal"=West_bengal,
           "Delhi"=Delhi,
           "Telangana"=Telangana,
           "Uttrakhand"=Uttrakhand,
           "TamilNadu"=TamilNadu,
           "Kerala"=Kerala,
           "Rajasthan"=Rajasthan,
           "Odisha"=Odisha,
           "Maharastra"=Maharastra,
           "Andaman_and_Nicobar"=Andaman_and_Nicobar
           
           
           
           
    )
  })
  
  output$data_type3 <- renderUI({
    data <- datasetInput3()
    selectInput("data_type3", "Select the tour place", choices = data$Data_Type)
  })
  
  output$pictures3 <- renderUI({
    data <- datasetInput3()
    pictures_url3 <- data[data$Data_Type == input$data_type3, "Picture_URL"]
    
    if (is.null(pictures_url3) || length(pictures_url3) == 0) {
      return(NULL)
    }
    
    pictures3 <- lapply(pictures_url3, function(url) {
      tags$img(src = url)
    })
    
    div(pictures3)
  })
  
  output$content3 <- renderDT({
    data <- datasetInput3()
    datatable(data)
  })
  
  
}

shinyApp(ui, server)

```
# Questions 

1. What are the current trends in tourism in India?

2. How "Tourism in India" contributes to the economic growth in India?

3. What is the role of technology in enhancing the tourist experience in India?

4. How can language barriers be managed for tourists visiting from non-English speaking countries?

5. What are the cultural sensitivities and customs that need to be considered when promoting tourism in India?

6. What are the environmental impacts of increased tourism in India and how can they be mitigated?

7. What are the limitations in terms of availability and affordability of accommodation for tourists in India?

8. How can the issue of over tourism in certain Indian destinations be managed?

9. How does the security issues impact tourism in India and what measures are inplace to insure the safety of Tourists?

10. How does the global pandemic affect the tourism industry in India?

11. How can infrastructure and transportation be improved to handle the influx of tourists in popular Indian destinations?

12. What are the roles of different stakeholders, including government, private sector, and local communities, in shaping Indian tourism?

13. How do political and social issues affect the tourism industry in India?

# Challenges and Limitations

Challenges faced during app development and discuss potential limitations.

The data is too much nasty for Web Scrapping. Most of the time the name of the variables are not same so we have to set the variable names carefully.

Numerical dataset is not available so we are not able to do data analysis sufficiently.

# Conclusion

Summarizing the main points of the report and emphasize the importance of the "Tourism in India" Shiny app.

Our main objective is to show the top ten most favorable places in states and main parts of India.

We also scrape some tables that can explain the tourism more in India.

The following tables are:-

Foreign tourist arrivals in India (1997–2022).

Foreign exchange earnings from tourism in India (1997–2020).

Source countries for foreign tourist arrivals in India in 2019.

Share of top 10 states/UT's of India in number of foreign tourist visits in 2017.

Share of top 10 states/UT's of India in number of domestic tourist visits in 2017.

States Table

Main Parts of India(North,South,Central,East,West,North East)

We also add description on the final table.
If you want travel any place then you just click on Details to see the Description of that place.

We also scrap data related to Motorbike Tour which is most famous among the youngster.

If you want to travel Month wise in India you just select the month and the description will be seen.

Finally we try to make an app that is user friendly and easy to explain all the things related to Tourism(one of them is top ten most favorable places.)

# Future Work
Provide suggestions for future improvements or additional features that can enhance the app.

We also want to add the description of the place below the photo make our shiny app more attractive and useful for enthusiastic tourists.

# References
It utilizes data obtained from web sources such as Wikipedia

("<https://en.wikipedia.org/wiki/Tourism_in_India>"),

("<https://www.tourism-of-india.com/travel-by-month.html>"),

("<https://www.thrillophilia.com/motorcycle-tours-in-india>"),

("<https://www.tourism-of-india.com/travel-by-month.html>"). 

The app makes use of several R packages, including `shiny`, `rvest`, `dplyr`, `ggplot2`, and `DT`.

# THANK YOU
